Patient-Specific Neural Field Modeling from Mirco-Electrode Data

### 2010-07-21 ltx/data_paper/DataPaper.tex
change to scaling in plots

\title{Patient-Specific Neural Field Modeling from Mirco-Electrode Data}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Jacob A. Donoghue, Sydney S. Cash, David B. Grayden and Visakan Kadirkamanathan  }

@@

\section{Estimation Algorithm}
\subsection{State-Space Model}
The state-space model is given by
 \mathbf x_{t+1}=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r)

@@

 \mathbf y_t=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t
and the non-linear map $q(.)$ is defined as
\begin{equation}\label{eq:QmatrixForSigmapoints}
	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}'.
\begin{equation}\label{eq:DefPsi}
	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
$ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.
\subsection{$\mathcal Q$-function}
Given a joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over observed variables $\mathbf Y$ and hidden variables $\mathbf X$ governed by parameters $\boldsymbol \theta$ and $\xi$, the goal is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$. It is often difficult to maximize the likelihood  $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly, however by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute 
a sequence of parameter estimates  that converges on the maximum likelihood parameter estimate. Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
 p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0)
\label{eq:jointdistribution}
The $\mathcal Q$-function can be written in terms of joint distribution components as

>>>>

\title{Patient-Specific Neural Field Modeling from Mirco-Electrode Data}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
 David B. Grayden and Visakan Kadirkamanathan  }

@@

\section{Estimation Algorithm}
\subsection{State-Space Model}
The state-space model is given by
\begin{align}
 \mathbf x_{t+1}&=q(\mathbf x_t)\boldsymbol\theta+\xi \mathbf x_t+\boldsymbol e_t(\mathbf r) \\
 \mathbf y_t&=\mathbf C \mathbf x_t+\boldsymbol \epsilon_t
\end{align}
and the nonlinear function, $q(\cdot)$, is defined as
\begin{equation}\label{eq:QmatrixForSigmapoints}
	q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}',
\end{equation}
where
\begin{equation}\label{eq:DefPsi}
	\boldsymbol{\Psi}(\mathbf{r}') \triangleq T_s\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\psi}^{\top} (\mathbf{r}'-\mathbf{r})d\mathbf{r}},
\end{equation}
$ \boldsymbol e_t(\mathbf r)\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_e(\mathbf r,\mathbf r'))$ is temporally white and spatially colored disturbance and  $\boldsymbol\epsilon_t\sim \mathcal N(\mathbf 0,\boldsymbol\Sigma_{\epsilon})$ is a white noise process.

\subsection{$\mathcal Q$-function}
The goal of the M-step is to maximize the likelihood function $p(\mathbf Y;\boldsymbol \theta,\xi)$ given the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ over the observed variables $\mathbf Y$ and hidden variables $\mathbf X$ that is governed by parameters $\boldsymbol \theta$ and $\xi$. Unfortunately, it is often difficult to maximize the likelihood $p(\mathbf Y;\boldsymbol \theta,\xi)$ directly. However, by using the relationship between $p(\mathbf Y;\boldsymbol \theta,\xi)$ and $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ it is possible to compute a sequence of parameter estimates that converges on the maximum likelihood parameter estimate.

Expanding the joint distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)$ we have
\begin{equation}\label{eq:jointdistribution}
 p(\mathbf X,\mathbf Y;\boldsymbol \theta,\xi)=\prod_{t=1}^{T} p(\mathbf y_t|\mathbf x_t)p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)p(\mathbf x_0).

@@

The $\mathcal Q$-function, or lower bound on the likelihood, can be written in terms of joint distribution components as
